Using Traffic Analysis to Identify the Second Generation Onion Router

### 2011-06-26 thesis/thesis.tex
Clean up title page a bit, remove page number
Add back in the fourth question from the proposal
Wording improvements to the introduction

% Setup the variables for the title page
\title{Using traffic analysis to identify The Second Generation Onion Router}
\author{John Barker}
\department{School of Computer and Security Science}
\school{Edith Cowan University}
\degree{Computer Science (Honours)}
\email{jebarker@our.ecu.edu.au}
\studentid{0991300}
\supervisor{Dr Andrew Woodward}
\supervisor{Mr Peter Hannay}
\supervisor{Mr Patryk Szewczyk}

% Begin document
\begin{document}
\maketitle

@@

This seminal paper spurred research into new techniques for providing anonymity
and privacy for digital networks. Remailers such as Babel
\parencite{Gulcu:1996p1662} and Mixminion \parencite{Danezis:2003ys} employed a
mix to deliver anonymous email. Research produced designs that yielded
mathematically provable anonymity
\parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303} and networks that
degrade gracefully when subject to attack, so called robust anonymity
\parencite{Waidner:1989p5870,Jakobsson:1998p5137}. Designs such as MorphMix
\parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
\parencite{P5Sherwood:2005p5872} aimed to provide anonymity features to
peer-to-peer (P2P) networks.

Providing resistance to blocking or censorship comes in many forms. The People's
Republic of China operates a sophisticated Internet firewall capable of blocking
requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
This system is often referred to as the Great Firewall of China. Resisting this
system can involve ignoring spurious reset packets injected into the stream of
forbidden communications \parencite{springerlink:10.1007/11957454-2}, or be as
simple as accessing data through an encrypted proxy as is done in FreeGate
\parencite{Smart:2008kx}.

More sophisticated circumvention tend to be based on anonymity providing
designs, \textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship
resistant system built on top of AN.ON
\parencite{springerlink:10.1007/3-540-44702-4-7}. Publishing systems such as
Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
aim to provide censorship resistance as well as anonymity. Infranet uses
steganography to hide sensitive messages in innocuous content Infranet
\parencite{Feamster:2002p307}.

@@

\begin{enumerate*}
  \item Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?
  \item Can Tor traffic be identified using automated matching techniques?
  \item Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?
\end{enumerate*}

>>>>

% Setup the variables for the title page
\title{Using Traffic Analysis to Identify the Second Generation Onion Router}
\author{John Barker}
\department{School of Computer and Security Science}
\school{Edith Cowan University}
\degree{Computer Science (Honours)}
\email{jebarker@our.ecu.edu.au}
\studentid{0991300}
\supervisor{Dr Andrew Woodward}
\supervisor{Mr Peter Hannay}
\supervisor{Mr Patryk Szewczyk}

% Begin document
\begin{document}
\doublespacing
\maketitle

@@

This seminal paper spurred research into new techniques for providing anonymity
and privacy to digital networks. Remailers such as Babel
\parencite{Gulcu:1996p1662} and Mixminion \parencite{Danezis:2003ys} employed a
mix to deliver anonymous email. Research produced designs that yielded
mathematically provable anonymity
\parencite{Chaum:1988p5869,Waidner:1989p5870,Berman:2004p303} and networks that
degrade gracefully when subject to attack, so called robust anonymity
\parencite{Waidner:1989p5870,Jakobsson:1998p5137}. Designs such as MorphMix
\parencite{Rennhard:2002p4559}, Tarzan \parencite{Freedman:2002kx} and P5
\parencite{P5Sherwood:2005p5872} aimed to provide anonymity features to
peer-to-peer (P2P) networks.

Providing resistance to blocking or censorship comes in many forms. The People's
Republic of China operates a sophisticated Internet firewall capable of blocking
requests to forbidden information \parencite{The-OpenNet-Initiative:2009uq}.
This system is often referred to as the Great Firewall of China. Resisting this
system can involve ignoring spurious reset packets injected into the stream of
forbidden communications \parencite{springerlink:10.1007/11957454-2}, or
accessing censored sites through an encrypted proxy such as FreeGate
\parencite{Smart:2008kx}.

More sophisticated censorship circumvention involves anonymous digital networks.
\textcite{Kopsell:2004:ABR:1029179.1029197} describes a censorship resistant
system built on top of AN.ON \parencite{springerlink:10.1007/3-540-44702-4-7}.
Freedom \parencite{Goldberg:1999p2231} and Freenet \parencite{Clarke:2001p2435}
provide a document publication network that aims to provide censorship
resistance as well as anonymity. Infranet uses steganography to hide sensitive
messages in images transferred as part of anodyne HTTP sessions
\parencite{Feamster:2002p307}. However many of these systems have not attained
significant public exposure.

@@

\begin{enumerate*}
  \item Can Tor traffic be distinguished from other network traffic that uses
    similar or the same encryption and protocols?
  \item Can Tor traffic be identified using automated matching techniques?
  \item Does Tor traffic have characteristics that make it readily distinguishable using
    heuristics based matching?
  \item How long does a user have to be connected to the network before a
    confident match can be made?
\end{enumerate*}
